---
title: "DeepSpatialAnalysis"
author: "Juan P Barraza"
date: "11/29/2021"
output: html_document
---
In here I am aiming to do a more in depth analysis of the spatial data
```{r setup, include=FALSE}
```{r biomass per slice}
#this was taken from "Microscopy data clean.Rmd" 
GetSliceData<-function(){#import all experiments at once
  folder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Results per slice'
   fileList<-list.files(path = folder, full.names = TRUE)
   growthDf<-data.frame()
   for (aggList in 1:length(fileList)){
     fileName<-str_split(basename(fileList[aggList]), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
     attrList<-str_split(fileName,"_")[[1]]
     growthDf<-rbind(growthDf,ReadSliceFile(fileList[aggList],attrList[2],attrList[1],attrList[3], fileName))
     }
   return(growthDf)
}
  
ReadSliceFile<-function(file, timepoint, condition, replicate, sampleCode){#make a dataframe of the aggregate size list and add experimental parameters
  print(file)
   datos <-read.csv(file, header = F)  
   colnames(datos)<-c('Voxels', 'Channel', 'Slice') 
   datos<-datos %>% mutate(TimePoint = timepoint) 
   datos<-datos %>% mutate(Condition = condition)
   datos<-datos %>% mutate(Replicate = replicate)
   datos<-datos %>% mutate(SampleCode = sampleCode)
   datos$Replicate<-as.factor(datos$Replicate)
   datos$Condition<-as.factor(datos$Condition)
   datos$TimePoint<-as.factor(datos$TimePoint)
   datos$SampleCode<-as.factor(datos$SampleCode)
   return(datos)
}

#Input data
#####
#get data from csv file
slicedData<-GetSliceData()
#get metadata
metaData.df <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/images metadata.csv', header = TRUE)
metaData.df$SampleCode<-as.factor(metaData.df$SampleCode)

#merge files
metaData.df<-metaData.df %>% select(SampleCode, Position, Region, Zdim, xyDim,xySize)
sliceDataMeta<-metaData.df %>%  merge(slicedData, by = "SampleCode")
#clean up
remove <- bind_rows(sliceDataMeta %>% filter(Channel == 2 & Condition == "mono"),
                    sliceDataMeta %>% filter(Channel == 1 & Condition == "pawt"),
                    sliceDataMeta %>% filter(Channel == 1 & Condition == "paphz"),
                    sliceDataMeta %>% filter(Channel == 1 & Condition == "papqsL"))

sliceDataMeta <- anti_join(sliceDataMeta, remove)

sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "mono_d1_03")
sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "phz_d4_14") #didnt make it to this dataset but still making sure
sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pqsL_d4_02")
sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pqsL_d4_04")
sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pqsL_d4_10")
sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "wt_d4_07")
sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "papqsL_d4_02")
sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pawt_d4_05")
sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "phz_d4_06")

#rename or add variables
sliceDataMeta<-sliceDataMeta %>% mutate(Species = recode(Channel,"1" ='S. aureus',"2" ='P. aeruginosa',"3" ='Host'))
sliceDataMeta$Condition<- factor(sliceDataMeta$Condition, levels = c("mono", "pawt","papqsL", "paphz", "wt", "pqsL", "phz"),
                                  labels = c('Sa mono', 'Pa wt mono','pqsL mono','phz mono','wt co', 'pqsL co', 'phz co'))
sliceDataMeta$TimePoint <- factor(sliceDataMeta$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))
sliceDataMeta<-sliceDataMeta %>% mutate(Culture = recode(Condition, 'Sa mono' = "mono", 'Pa wt mono' = "mono",'pqsL mono'= "mono",'phz mono'= "mono",'wt co'= "co", 'pqsL co'= "co", 'phz co'= "co"))
sliceDataMeta<-sliceDataMeta%>% mutate(Strain = recode(Condition, 'Sa mono' = "Sa", 'Pa wt mono' = "wt",'pqsL mono'= "pqsL",'phz mono'= "phz",'wt co'= "wt", 'pqsL co'= "pqsL", 'phz co'= "phz"))

#remove host channel, add Height (current), Total Heightuseful metrics
sliceDataMeta<-sliceDataMeta%>% filter(!Channel == "3") %>% mutate(CurrentHeight = Zdim*Slice, Biomass = Voxels*Zdim*xyDim*xyDim) %>% group_by(SampleCode)%>% mutate(TotalHeight = max(CurrentHeight))%>%ungroup() %>% group_by(SampleCode, Species) %>% mutate(SpeciesBiomass = sum(Biomass)) %>% ungroup()
sliceDataMeta<-sliceDataMeta %>% group_by(SampleCode)%>% mutate(TotalVolume = TotalHeight*xySize*xySize, TotalBiomass = sum(Biomass)) %>% ungroup() %>% 
  mutate(TotalRatio = TotalBiomass/TotalVolume, SpeciesRatio = SpeciesBiomass/TotalVolume, currentRatio = Biomass/(CurrentHeight*xySize*xySize))

sliceDataSumary<-sliceDataMeta %>% group_by(SampleCode,Species,TimePoint, Strain, Culture,TotalBiomass,TotalVolume,TotalRatio)%>% summarise() %>% unique()
#SpeciesBiomass is separated by species, TotalBiomass is for both

ggplot()+
  geom_point(data = sliceDataSumary,aes(x=SampleCode,y=TotalRatio, color = Culture, shape = Strain),size=4)+
  geom_hline(aes(yintercept = 0.5))+
  geom_hline(aes(yintercept = 0.1))+
  geom_hline(aes(yintercept = 0.01))+
  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))


#calculate relative biomass
##For all samples

sliceDataMetaAll<-sliceDataMeta%>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100) 

sliceDataSumary<-sliceDataMeta %>% group_by(SampleCode, TimePoint, Strain, Culture, MaxHeight)%>% summarise() %>% unique()

sliceDataClean<-sliceDataMeta %>% filter(MaxHeight>60) %>% filter(Height<60) %>% filter(TimePoint=="Day 4") %>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100) 

#####
#Plot Data
#####
ggplot()+
  #geom_point(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color = Condition, group = Replicate),size=.5)+
  geom_smooth(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color =Condition),size=2)+
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
  theme_cowplot()+
  scale_color_brewer(palette = "Set1")+
  ylim(0,26)+
  facet_grid(Channel~TimePoint)+
  panel_border() +
  coord_flip()
  theme(plot.title = element_text(hjust = 0.5))
#####
#Filter by Max height of the sample
#####  
  #graph the samples height
  ggplot()+
    geom_col(data = sliceDataSumary %>% filter(TimePoint=="Day 4"),aes(x=SampleCode,y=MaxHeight, color = Strain, fill =Culture ),size=2)+
    geom_hline(yintercept = 50)+
    labs(title ="title")+
    scale_color_brewer(palette = "Set2")+
    scale_fill_brewer(palette = "Set1")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
#####
PlotZsliceSa<-function(){  
  ggplot()+
    geom_smooth(data = sliceDataClean %>% filter(Species == "S. aureus"),aes(y=NormBiomass,x=Height, color = Region),size=2, alpha = .1)+
    #geom_point(data = sliceDataClean%>% filter(Species == species),aes(y=NormBiomass,x=Height, color = Region),size=1, alpha = .5)+
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
    theme_cowplot()+
    scale_color_brewer(palette = "Set1")+
    facet_grid(Strain~.)+
    scale_shape_manual(values = c(1, 3))+
    panel_border() +
    coord_flip()+
    theme(plot.title = element_text(hjust = 0.5))}
PlotZslicePa<-function(){  
  ggplot()+
    geom_smooth(data = sliceDataClean %>% filter(Species == "P. aeruginosa") %>% filter(Culture=="co"),aes(y=NormBiomass,x=Height, color = Region),size=2, alpha = .1)+
    #geom_point(data = sliceDataClean%>% filter(Species == species),aes(y=NormBiomass,x=Height, color = Region),size=1, alpha = .5)+
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
    theme_cowplot()+
    scale_color_brewer(palette = "Set1")+
    facet_grid(Strain~.)+
    scale_shape_manual(values = c(1, 3))+
    panel_border() +
    coord_flip()+
    theme(plot.title = element_text(hjust = 0.5))}
PlotZslicePa()
PlotZsliceSa()

sliceDataClean$Strain <- factor(sliceDataClean$Strain, levels = c("Sa","wt","pqsL","phz"),labels = c("Sa", "wild-type", paste0(bquote(Delta),"pqsL"), expression(paste(alpha,"phz"))))
PlotZsliceBth<-function(){  
  ggplot()+
    geom_smooth(data = sliceDataClean %>% filter(Culture=="co", Strain == "wt"),aes(y=NormBiomass,x=Height, color = Species ),size=2, alpha = .1)+
    #geom_point(data = sliceDataClean%>% filter(Species == species),aes(y=NormBiomass,x=Height, color = Region),size=1, alpha = .5)+
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
    theme_cowplot()+
    scale_color_brewer(palette = "Set1",breaks=c("P. aeruginosa","S. aureus"), 
                   labels = c(bquote(paste(italic("P. aeruginosa"))), bquote(paste(italic("S. aureus")))))+
    labs(color ="", y = "Percent Biomass", x = bquote(paste("Height (", mu*"m)")))+
    facet_grid(.~Region)+
    scale_shape_manual(values = c(1, 3))+
    panel_border() +
    coord_flip()+
    theme(plot.title = element_text(hjust = 0.5),strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}
labels = c(bquote(paste(italic("P. aeruginosa"), " wt")), bquote(paste(italic(Delta*"pqsL"))))
paste0("(1000, ",bquote("\U221E"), ")")
PlotZsliceBth()

```
